Assessing Virulence by MCG

### 2017-09-06 doc/RMD/MCG-virulence.Rmd
update MCG virulence; add ggforce
APPARENTLY agricolae has change such that HSD.test
has completely different output, messing up my flow
>:(

Oh, I also am using geom_sina and crossbars for the
figure.

grps %>% 
  dplyr::rename(MCG = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  readr::write_csv(path = "results/tables/MCG-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.05, 0.3, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 31)
```

@@

```{r fig.width = 5, fig.height = 3.75}
set.seed(2017-06-29)
region_dat <- dat %>%
  group_by(Region) %>%
  filter(n() > 5) %>%
  mutate(mean_sev = mean(Severity)) %>%
  mutate(Source = ifelse(Source == "wmn", "wmn", "other")) %>%
  arrange(desc(mean_sev)) %>%
  ungroup() %>%
  mutate(Region = forcats::fct_inorder(Region)) %>%
  select(Region, Severity, Source)
ggplot(region_dat, aes(x = Region, y = Severity)) +
  geom_point(aes(fill = Source), 
             pch = 21, 
             position = position_jitter(width = 0.25), 
             alpha = 0.35) +
  geom_boxplot(alpha = 0.5) +
  scale_y_continuous(limits = c(1, 9), breaks = c(1, 3, 5, 7, 9), expand = c(0, 0.1)) +
  scale_fill_manual(values = rev(c("black", "white"))) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50")) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "top") +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines")) +
  labs(list(
    y = "Aggressiveness",
    x = "Region"
    ))
if (!interactive()){
  ggsave(file.path("results", "figures", "publication", "aggressiveness.pdf"),
         width = 88, units = "mm")
}
```

```{r anova2, fig.width = 4, fig.height = 8}
region_dat %>%
  group_by(Region) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity),
            `Median Aggressiveness` = median(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ Region, data = region_dat)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "Region", alpha = 0.05)$groups %>% 
  dplyr::rename(Region = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  readr::write_csv(path = "results/tables/Region-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```

@@

```{r anova3, fig.width = 4, fig.height = 8}
top_mlg %>%
  group_by(MLG) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ MLG, data = top_mlg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "MLG", alpha = 0.05)$groups %>% 
  dplyr::rename(MLG = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  readr::write_csv(path = "results/tables/MLG-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```

>>>>

grps %>% 
  tibble::rownames_to_column("MCG") %>%
  dplyr::rename(Group = groups) %>%
  dplyr::rename(`Mean Aggressiveness` = Severity) %>%
  readr::write_csv(path = "results/tables/MCG-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.05, 0.3, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 31)
```

@@

```{r fig.width = 5, fig.height = 3.75}
set.seed(2017-06-29)
region_dat <- dat %>%
  group_by(Region) %>%
  filter(n() > 5) %>%
  mutate(mean_sev = mean(Severity)) %>%
  mutate(Source = ifelse(Source == "wmn", "wmn", "producer field")) %>%
  arrange(desc(mean_sev)) %>%
  ungroup() %>%
  mutate(Region = forcats::fct_inorder(Region)) %>%
  select(Region, Severity, Source)

plot.median <- function(x) {
  m <- mean(x, na.rm = TRUE)
  c(y = m, ymin = m, ymax = m)
}

ggplot(region_dat, aes(x = Region, y = Severity)) +
  ggforce::geom_sina(aes(fill = Source), 
             pch = 21, 
             alpha = 0.4) +
  # geom_point(aes(fill = Source), 
  #            pch = 21, 
  #            position = position_jitter(width = 0.25), 
  #            alpha = 0.35) +
  # geom_boxplot(alpha = 0.5) +
  stat_summary(fun.data = "plot.median", geom = "errorbar", colour = "black", width = 0.6, size = 2, alpha = 0.5) +
  stat_summary(fun.data = "plot.median", geom = "errorbar", colour = "white", width = 0.5, size = 1, alpha = 1) +
  scale_y_continuous(limits = c(1, 9), breaks = c(1, 3, 5, 7, 9), expand = c(0, 0.1)) +
  scale_fill_manual(values = rev(c("black", "white"))) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50")) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "top") +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines")) +
  labs(list(
    y = "Aggressiveness",
    x = "Region"
    ))
if (!interactive()){
  ggsave(file.path("results", "figures", "publication", "aggressiveness.pdf"),
         width = 88, units = "mm")
}
```

```{r anova2, fig.width = 4, fig.height = 8}
region_dat %>%
  group_by(Region) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity),
            `Median Aggressiveness` = median(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ Region, data = region_dat)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "Region", alpha = 0.05)$groups %>% 
  tibble::rownames_to_column("Region") %>%
  dplyr::rename(Group = groups) %>%
  dplyr::rename(`Mean Aggressiveness` = Severity) %>%
  readr::write_csv(path = "results/tables/Region-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```

@@

```{r anova3, fig.width = 4, fig.height = 8}
top_mlg %>%
  group_by(MLG) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ MLG, data = top_mlg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "MLG", alpha = 0.05)$groups %>% 
  tibble::rownames_to_column("MLG") %>%
  dplyr::rename(Group = groups) %>%
  dplyr::rename(`Mean Aggressiveness` = Severity) %>%
  readr::write_csv(path = "results/tables/MLG-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```
